Do we need detailed demographic data to forecast plant population responses to climate change?

### 2016-08-29 manuscript/manuscript.Rmd
adds PBA R1 edits

To date, most empirical population modelers have relied on individual-level data, with few attempts to capitalize on population-level measures. An important exception was an effort by @Taylor2004 to model the population growth rate of an invasive species to identify the best strategies for invasion control. They used a "density-structured" model where the state variable is a discrete density state rather than a continuous density measure. Such models do not require individual-level demographic data and can adequately describe population dynamics. Building on @Taylor2004, @Freckleton2011 showed that density-structured models compare well to continuous models in theory, and @Queenborough2011 provide empirical evidence that density-structured models are capable of reproducing population dynamics at landscape spatial scales, even if some precision is lost when compared to fully continuous models. \textcolor{blue}{Density-structured models based on animal counts have also begun to find a home in dynamic species distribution models} [@Mieszkowska2013; @Hefley2016]. However, previous tests of density-structured population models have yet to assess their ability to forecast out-of-sample observations, and they have not included environmental covariates, which are necessary to forecast population responses to climate change.

@@

Materials and Methods
---------------------
### Overview of analysis
\textcolor{blue}{We used two types of data: individual-level data and percent cover data.
Using the individual-level data, we fit three vital rate regressions (survival, growth, and rectruitment) to build an Integral Projection Model (IPM) for simulating the plant populations.
Using the percent cover data we fit a simple, Gompertz population growth model, which we refer to as a quadrat-based model (QBM).
Both model types (IPM and QBM) were fit with and without climate covariates.
We used Bayesian ridge regression to weight the importance of each climate covariate.
We then performed cross-validation to assess each model's ability to predict out-of-sample data.
We compared the forecast accuracy ($\rho$, correlation between observations and predictions) and mean absolute error (MAE) between the IPM and the QBM to test our expectation that the IPM should outperform the QBM.
Lastly, we use in-sample forecasts to quantify each model's forecast horizon} [@Petchey2015].

@@

We fit all models using a hierarchical Bayesian approach. We focus on the main process and the model likelihood in what follows (full model descriptions are in the Supporting Information). For the likelihood models, $\textbf{y}^X$ is always the relevant vector of observations for vital rate *X* (*X* = *S*, *G*, *R*, or *P*) for survival, growth, recruitment, or population growth). For example, $\textbf{y}^S$ is a vector of 0s and 1s indicating whether a genet survives from *t* to *t+1*, or not, for all observation years and quadrats. All model parameters are species-specific, but we omit subscripts for species in model descriptions below to reduce visual clutter. For brevity, we only describe models with climate covariates included, but models without climate covariates are simply the models described below with the climate effects removed.

@@

### Forecast horizons
An important feature of any forecasting model is the rate at which forecast skill declines as the time between an observation and a forecast increases.
\textcolor{blue}{In particular, we are interested in the temporal distance at which forecast skill falls below a threshold: the so-called ecological forecast horizon} [@Petchey2015].
To assess the forecast horizons of our models, we initiate the forecast model with the population state at some time *t* and make sequential forecasts of the population at times $t+1, t+2, \dots, t+T$ where *T* is the maximum number of years between the initial year and the final year of our observations.
For example, if we initialize the forecast model with percent cover in 1940, we are able to make five forecasts up to the year 1945.
Forecast models are not re-initialized with observations between years.
Thus, in our current example, the model forecast for percent cover in 1941 has a forecast horizon of one year, the forecast in 1942 has a forecast horizon of two years, and so on.
We performed these simulations for all model types (IPM with/without climate; QBM with/without climate) using mean parameter values for all possible initial years.
For a given forecast distance, we averaged the correlation between forecasts and observations.
Note that our forecasts for the horizon analysis are all made using in-sample data because we used model fits from the full data set.
Nonetheless, our simulations offer insight into the differences among model forecast horizons.
\textcolor{blue}{We chose a forecast accuracy of $\rho = 0.5$ as our forecast proficiency threshold.
So, the forecast horizon is the temporal distance at which forecast accuracy falls below $\rho = 0.5$.}

@@

With climate covariates included \textcolor{blue}{and using mean parameter values, the accuracy of both models' forecasts declined as the distance between the last observation and the forecast increased}, but they did so at similar rates (Fig. 4).
The only exception is for *Poa secunda*, where QBM forecast accuracy remained steady as the \textcolor{blue}{temporal distance of the forecast increased}, whereas IPM forecast accuracy declined (Fig. 4).
\textcolor{blue}{The forecast horizons were short: forecast accuracy fell below $\rho$ = 0.5 after one year for the IPM for most species, and after four years, at most, for the QBM (Fig. 4).
Across the different temporal distances from the observation to the forecast, the IPM was never more accurate than the QBM (Table S23).
Likewise, the QBM was rarely more accurate the IPM, the only exception being for \emph{H. comata} at temporal distances of two ($t_{(115)}$ = 2.39, \emph{P} = 0.002) and three years ($t_{(98)}$ = 2.04, \emph{P} = 0.022) (Table S24).
There were some cases where the QBM was more accurate than the IPM for \emph{Poa secunda}, but neither model exceeded the forecast profieciency threshold by a large margin (Fig. 4, Table S24).}

@@

We also expected IPM forecast accuracy to decline at a lower rate than the QBM as the \textcolor{blue}{time between the last observation and the forecast increased.}
In principle, more mechanistic models should produce better predictions, especially under novel conditions [@Evans2012b; @Schindler2015b].
In our case, the IPM explicitly models the influence of weather on recruitment and survival, effects that may be poorly represented in the QBM because recruitment and survival mainly affect small plants that contribute little to year-to-year changes in percent cover.
Over time, the addition and subtraction of small plants can have large effects on population growth, thus, explicitly modeling these effects could contribute to a longer forecast horizon. 
However, we found no evidence \textcolor{blue}{that the forecast horizon for the IPM was greater than the QBM (Fig. 4).
On the contrary, the QBM tended to have a slightly longer forecast horizon than the IPM for most species (Fig. 4).
The QBM has fewer processes, thus it may better capture near term dynamics when populations do not fluctuate widely, as in our case.
When populations do not fluctuate widely, often the best forecast for population size at \emph{t+1} is the size at time \emph{t}.
Thus, a simpler model such as the QBM may be well-suited for predicting populations that fluctuate mildly around an equilibrium.}

Our comparison of a model based on individual-level data with one based on percent cover data is not an exhaustive test.
Understanding the reasons why the percent cover-based model matched the skill of a demographic model for our focal species may help us anticipate situations in which a percent-cover approach would fail. 
First, for none of our species did a climate covariate have a strong negative effect on one vital rate and a strong positive effect on a different vital rate (Fig. 3).
As noted by @Freckleton2011, complex age or stage structure can compromise predictions from models that aggregate over life-histories, and the same should be true when aggregating across vital rates with contrasting responses to climate drivers.
Second, our particular recruitment model is already so aggregated -- it averages across seed production, germination and establishment -- that it may fail to detect important demographic responses to climate, putting our individual-based model and percent cover model on more equal footing. 
More finely resolved recruitment data might help our individual-based model outperform the population-level model.
As advocated by @Freckleton2011, knowledge of a species' population ecology should guide the modeling approach.
\textcolor{blue}{Third, our percent cover data are essentially error-free because we were able to aggregate indiviual plant areas to calculate percent cover.
Percent cover data collected by typical sampling protocals (e.g., Daubenmire frames) will include error that may affect population forecasts due to misspecifing the initial conditions and/or biasing model parameters} [@Queenborough2011].
\textcolor{blue}{Thus, it may be that our percent cover model performed just as well as the individual-based model because percent cover was perfectly measured.
One way to account for such error is to develop a sampling model that relates the observations (estimated percent cover in a plot) to the true state (percent cover derived from individual plant measurements in the same plot)} [@Hobbs2015].

\textcolor{blue}{Although our main goal was to compare individual-based and population-level modeling approaches relative to one another, it is worth reflecting on the absolute forecasting skill of our models.
In particular, the forecast horizon of both models, defined as the time horizon at which the correlation between predictions and observations falls below $\rho = 0.5$, is less than five years for all species. 
Such short forecast horizons are not encouraging.}
\textcolor{blue}{Unfortunately, we have little to offer on how to improve population forecasts that has not already been proposed} [@Petchey2015; @Mouquet2015].
\textcolor{blue}{Longer time-series should improve our ability to detect exogenous drivers such as climate} [@Teller2016], \textcolor{blue}{and modeling larger spatial extents may reduce parameter uncertainty} [@Petchey2015].
\textcolor{blue}{We may also have to shift our perspective from making explicit point forecasts to making moving average forecasts} [@Petchey2015].
\textcolor{blue}{For example, IPMs are typically capable of estimating equilibrium abundances} [e.g., @Adler2012], \textcolor{blue}{which may be more appropriate for dynamic systems.}

>>>>

To date, most empirical population modelers have relied on individual-level data, with few attempts to capitalize on population-level measures. An important exception was an effort by @Taylor2004 to model the population growth rate of an invasive species to identify the best strategies for invasion control. They used a "density-structured" model where the state variable is a discrete density state rather than a continuous density measure. Such models do not require individual-level demographic data and can adequately describe population dynamics. Building on @Taylor2004, @Freckleton2011 showed that density-structured models compare well to continuous models in theory, and @Queenborough2011 provide empirical evidence that density-structured models are capable of reproducing population dynamics at landscape spatial scales, even if some precision is lost when compared to fully continuous models. However, previous tests of density-structured population models have yet to assess their ability to forecast out-of-sample observations, and they have not included environmental covariates, which are necessary to forecast population responses to climate change.

<!--
\textcolor{blue}{Density-structured models based on animal counts have also begun to find a home in dynamic species distribution models} [@Mieszkowska2013; @Hefley2016].
-->

@@

Materials and Methods
---------------------
### Overview of analysis
\textcolor{blue}{We used two types of data: individual-level data and percent cover data.
Using the individual-level data, we fit three vital rate regressions (survival, growth, and rectruitment) to build an Integral Projection Model (IPM) for simulating the plant populations.
Using the percent cover data we fit a simple, Gompertz population growth model, which we refer to as a quadrat-based model (QBM).
For both model types (IPM and QBM), we fit and simulate versions of the model with and without climate covariates.
We used Bayesian ridge regression to weight the importance of each climate covariate.
We then performed cross-validation to assess each model's ability to predict out-of-sample data.
We compared the forecast accuracy ($\rho$, correlation between observations and predictions) and mean absolute error (MAE) between the IPM and the QBM to test our expectation that the IPM should outperform the QBM.
Lastly, we use in-sample forecasts to quantify each model's forecast horizon} [@Petchey2015].

@@

We fit all models using a hierarchical Bayesian approach. We focus on the main process and the model likelihood in what follows (full model descriptions are in the Supporting Information). For the likelihood models, $\textbf{y}^X$ is always the relevant vector of observations for vital rate *X* (*X* = *S*, *G*, *R*, or *P* for survival, growth, recruitment, or population growth). For example, $\textbf{y}^S$ is a vector of 0s and 1s indicating whether a genet survives from *t* to *t+1*, or not, for all observation years and quadrats. All model parameters are species-specific, but we omit subscripts for species in model descriptions below to reduce visual clutter. For brevity, we only describe models with climate covariates included, but models without climate covariates are simply the models described below with the climate effects removed.

@@

### Forecast horizons
An important feature of any forecasting model is the rate at which forecast skill declines as the time between an observation and a forecast increases.
\textcolor{blue}{In particular, we are interested in the temporal distance at which forecast skill falls below a threshold: the so-called ecological forecast horizon} [@Petchey2015].
To assess the forecast horizons of our models, we initiate the forecast model with the population state at some time *t* and make sequential forecasts of the population at times $t+1, t+2, \dots, t+T$ where *T* is the maximum number of years between the initial year and the final year of our observations.
For example, if we initialize the forecast model with percent cover in 1940, we are able to make five forecasts up to the year 1945.
Forecast models are not re-initialized with observations between years.
Thus, in our current example, the model forecast for percent cover in 1941 has a forecast horizon of one year, the forecast in 1942 has a forecast horizon of two years, and so on.
We performed these simulations for all model types (IPM with/without climate; QBM with/without climate) using mean parameter values for all possible initial years.
For a given forecast distance, we averaged the correlation between forecasts and observations.
Note that our forecasts for the horizon analysis are all made using in-sample data because we used model fits from the full data set.
Nonetheless, our simulations offer insight into the differences among model forecast horizons.
\textcolor{blue}{We chose an arbitrary forecast accuracy of $\rho = 0.5$ as our forecast proficiency threshold.
For basic research on forecasting, arbitrary proficiency thresholds suffice for comparative purposes} [@Petchey2015], \textcolor{blue}{and $\rho = 0.5$ represents the point at which about 25% of the variance in observations is explained by the predictions.
So, the forecast horizon is the temporal distance at which forecast accuracy falls below $\rho = 0.5$.}

@@

With climate covariates included \textcolor{blue}{and using mean parameter values, the accuracy of both models' forecasts declined as the distance between the last observation and the forecast increased}, but they did so at similar rates (Fig. 4).
The only exception is for *Poa secunda*, where QBM forecast accuracy remained steady as the \textcolor{blue}{temporal distance of the forecast increased}, whereas IPM forecast accuracy declined (Fig. 4).
\textcolor{blue}{The forecast horizons were short: forecast accuracy fell below $\rho$ = 0.5 after one year for the IPM for most species, and after four years, at most, for the QBM (Fig. 4).
Across the different temporal distances from the observation to the forecast, the IPM was never more accurate than the QBM (\emph{P} > 0.05 for all one-sided \emph{t}-tests, Table S23).
Likewise, the QBM was rarely more accurate the IPM, the only exception being for \emph{H. comata} at temporal distances of two ($t_{(115)}$ = 2.39, \emph{P} = 0.002) and three years ($t_{(98)}$ = 2.04, \emph{P} = 0.022) (Table S24).
There were some cases where the QBM was more accurate than the IPM for \emph{Poa secunda}, but neither model exceeded the forecast profieciency threshold by a large margin (Fig. 4, Table S24).}

@@

We also expected IPM forecast accuracy to decline at a lower rate than the QBM as the \textcolor{blue}{time between the model initialization and the forecast increased.}
In principle, more mechanistic models should produce better predictions, especially under novel conditions [@Evans2012b; @Schindler2015b].
In our case, the IPM explicitly models the influence of weather on recruitment and survival, effects that may be poorly represented in the QBM because recruitment and survival mainly affect small plants that contribute little to year-to-year changes in percent cover.
Over time, the addition and subtraction of small plants can have large effects on population growth, thus, explicitly modeling these effects could contribute to a longer forecast horizon. 
However, we found no evidence \textcolor{blue}{that the forecast horizon for the IPM was greater than the QBM (Fig. 4).
On the contrary, the QBM tended to have a slightly longer forecast horizon than the IPM for most species (Fig. 4).
The QBM has fewer processes and parameters, which can reduce bias due to parameter uncertainty.
Thus, the QBM may better capture near term dynamics when populations do not fluctuate widely, as in our case.}

Our comparison of a model based on individual-level data with one based on percent cover data is not an exhaustive test.
Understanding the reasons why the percent cover-based model matched the skill of a demographic model for our focal species may help us anticipate situations in which a percent-cover approach would fail. 
First, for none of our species did a climate covariate have a strong negative effect on one vital rate and a strong positive effect on a different vital rate (Fig. 3).
As noted by @Freckleton2011, complex age or stage structure can compromise predictions from models that aggregate over life-histories, and the same should be true when aggregating across vital rates with contrasting responses to climate drivers.
Second, our particular recruitment model is already so aggregated -- it averages across seed production, germination and establishment -- that it may fail to detect important demographic responses to climate, putting our individual-based model and percent cover model on more equal footing. 
More finely resolved recruitment data might help our individual-based model outperform the population-level model.
As advocated by @Freckleton2011, knowledge of a species' population ecology should guide the modeling approach.
\textcolor{blue}{Third, our percent cover data are essentially error-free because we were able to aggregate indiviual plant areas to calculate percent cover.
Percent cover data collected by typical sampling methods (e.g., Daubenmire frames) will include error that may affect population forecasts due to misspecifing the initial conditions and/or biasing model parameters} [@Queenborough2011].
\textcolor{blue}{Percent cover models based on data containing more measurement error than ours might perform worse in comparison with individual-based models.
One way to account for such error is to develop a sampling model that relates the observations (estimated percent cover in a plot) to the true state (percent cover derived from individual plant measurements in the same plot)} [@Hobbs2015].

\textcolor{blue}{Although our main goal was to compare individual-based and population-level modeling approaches relative to one another, it is worth reflecting on the absolute forecasting skill of our models.
In particular, the forecast horizon of both models, defined as the time horizon at which the correlation between predictions and observations falls below $\rho = 0.5$, is less than five years for all species. 
Such short forecast horizons are not encouraging.}
\textcolor{blue}{Unfortunately, we have few ideas about how to improve population forecasts that have not already been proposed} [@Petchey2015; @Mouquet2015].
\textcolor{blue}{Longer time-series should improve our ability to detect exogenous drivers such as climate} [@Teller2016], \textcolor{blue}{and modeling larger spatial extents may reduce parameter uncertainty} [@Petchey2015].
\textcolor{blue}{We may also have to shift our perspective from making explicit point forecasts to making moving average forecasts} [@Petchey2015].
\textcolor{blue}{Whether the poor predictive ability of our models impacts their comparison relative to one another is an open question}.

### 2016-08-29 manuscript/manuscript.tex
adds PBA R1 edits

To date, most empirical population modelers have relied on
individual-level data, with few attempts to capitalize on
population-level measures. An important exception was an effort by
Taylor and Hastings (2004) to model the population growth rate of an
invasive species to identify the best strategies for invasion control.
They used a ``density-structured'' model where the state variable is a
discrete density state rather than a continuous density measure. Such
models do not require individual-level demographic data and can
adequately describe population dynamics. Building on Taylor and Hastings
(2004), Freckleton et al. (2011) showed that density-structured models
compare well to continuous models in theory, and Queenborough et al.
(2011) provide empirical evidence that density-structured models are
capable of reproducing population dynamics at landscape spatial scales,
even if some precision is lost when compared to fully continuous models.
\textcolor{blue}{Density-structured models based on animal counts have also begun to find a home in dynamic species distribution models}
(Mieszkowska et al. 2013, Hefley and Hooten 2016). However, previous
tests of density-structured population models have yet to assess their
ability to forecast out-of-sample observations, and they have not
included environmental covariates, which are necessary to forecast
population responses to climate change.

@@

\textcolor{blue}{We used two types of data: individual-level data and percent cover data.
Using the individual-level data, we fit three vital rate regressions (survival, growth, and rectruitment) to build an Integral Projection Model (IPM) for simulating the plant populations.
Using the percent cover data we fit a simple, Gompertz population growth model, which we refer to as a quadrat-based model (QBM).
Both model types (IPM and QBM) were fit with and without climate covariates.
We used Bayesian ridge regression to weight the importance of each climate covariate.
We then performed cross-validation to assess each model's ability to predict out-of-sample data.
We compared the forecast accuracy ($\rho$, correlation between observations and predictions) and mean absolute error (MAE) between the IPM and the QBM to test our expectation that the IPM should outperform the QBM.
Lastly, we use in-sample forecasts to quantify each model's forecast horizon}
(Petchey et al. 2015).

@@

We fit all models using a hierarchical Bayesian approach. We focus on
the main process and the model likelihood in what follows (full model
descriptions are in the Supporting Information). For the likelihood
models, \(\textbf{y}^X\) is always the relevant vector of observations
for vital rate \emph{X} (\emph{X} = \emph{S}, \emph{G}, \emph{R}, or
\emph{P}) for survival, growth, recruitment, or population growth). For
example, \(\textbf{y}^S\) is a vector of 0s and 1s indicating whether a
genet survives from \emph{t} to \emph{t+1}, or not, for all observation
years and quadrats. All model parameters are species-specific, but we
omit subscripts for species in model descriptions below to reduce visual
clutter. For brevity, we only describe models with climate covariates
included, but models without climate covariates are simply the models
described below with the climate effects removed.

@@

An important feature of any forecasting model is the rate at which
forecast skill declines as the time between an observation and a
forecast increases.
\textcolor{blue}{In particular, we are interested in the temporal distance at which forecast skill falls below a threshold: the so-called ecological forecast horizon}
(Petchey et al. 2015). To assess the forecast horizons of our models, we
initiate the forecast model with the population state at some time
\emph{t} and make sequential forecasts of the population at times
\(t+1, t+2, \dots, t+T\) where \emph{T} is the maximum number of years
between the initial year and the final year of our observations. For
example, if we initialize the forecast model with percent cover in 1940,
we are able to make five forecasts up to the year 1945. Forecast models
are not re-initialized with observations between years. Thus, in our
current example, the model forecast for percent cover in 1941 has a
forecast horizon of one year, the forecast in 1942 has a forecast
horizon of two years, and so on. We performed these simulations for all
model types (IPM with/without climate; QBM with/without climate) using
mean parameter values for all possible initial years. For a given
forecast distance, we averaged the correlation between forecasts and
observations. Note that our forecasts for the horizon analysis are all
made using in-sample data because we used model fits from the full data
set. Nonetheless, our simulations offer insight into the differences
among model forecast horizons.
\textcolor{blue}{We chose a forecast accuracy of $\rho = 0.5$ as our forecast proficiency threshold.
So, the forecast horizon is the temporal distance at which forecast accuracy falls below $\rho = 0.5$.}

@@

With climate covariates included
\textcolor{blue}{and using mean parameter values, the accuracy of both models' forecasts declined as the distance between the last observation and the forecast increased},
but they did so at similar rates (Fig. 4). The only exception is for
\emph{Poa secunda}, where QBM forecast accuracy remained steady as the
\textcolor{blue}{temporal distance of the forecast increased}, whereas
IPM forecast accuracy declined (Fig. 4).
\textcolor{blue}{The forecast horizons were short: forecast accuracy fell below $\rho$ = 0.5 after one year for the IPM for most species, and after four years, at most, for the QBM (Fig. 4).
Across the different temporal distances from the observation to the forecast, the IPM was never more accurate than the QBM (Table S23).
Likewise, the QBM was rarely more accurate the IPM, the only exception being for \emph{H. comata} at temporal distances of two ($t_{(115)}$ = 2.39, \emph{P} = 0.002) and three years ($t_{(98)}$ = 2.04, \emph{P} = 0.022) (Table S24).
There were some cases where the QBM was more accurate than the IPM for \emph{Poa secunda}, but neither model exceeded the forecast profieciency threshold by a large margin (Fig. 4, Table S24).}

@@

We also expected IPM forecast accuracy to decline at a lower rate than
the QBM as the
\textcolor{blue}{time between the last observation and the forecast increased.}
In principle, more mechanistic models should produce better predictions,
especially under novel conditions (Evans 2012, Schindler and Hilborn
2015). In our case, the IPM explicitly models the influence of weather
on recruitment and survival, effects that may be poorly represented in
the QBM because recruitment and survival mainly affect small plants that
contribute little to year-to-year changes in percent cover. Over time,
the addition and subtraction of small plants can have large effects on
population growth, thus, explicitly modeling these effects could
contribute to a longer forecast horizon. However, we found no evidence
\textcolor{blue}{that the forecast horizon for the IPM was greater than the QBM (Fig. 4).
On the contrary, the QBM tended to have a slightly longer forecast horizon than the IPM for most species (Fig. 4).
The QBM has fewer processes, thus it may better capture near term dynamics when populations do not fluctuate widely, as in our case.
When populations do not fluctuate widely, often the best forecast for population size at \emph{t+1} is the size at time \emph{t}.
Thus, a simpler model such as the QBM may be well-suited for predicting populations that fluctuate mildly around an equilibrium.}

Our comparison of a model based on individual-level data with one based
on percent cover data is not an exhaustive test. Understanding the
reasons why the percent cover-based model matched the skill of a
demographic model for our focal species may help us anticipate
situations in which a percent-cover approach would fail. First, for none
of our species did a climate covariate have a strong negative effect on
one vital rate and a strong positive effect on a different vital rate
(Fig. 3). As noted by Freckleton et al. (2011), complex age or stage
structure can compromise predictions from models that aggregate over
life-histories, and the same should be true when aggregating across
vital rates with contrasting responses to climate drivers. Second, our
particular recruitment model is already so aggregated -- it averages
across seed production, germination and establishment -- that it may
fail to detect important demographic responses to climate, putting our
individual-based model and percent cover model on more equal footing.
More finely resolved recruitment data might help our individual-based
model outperform the population-level model. As advocated by Freckleton
et al. (2011), knowledge of a species' population ecology should guide
the modeling approach.
\textcolor{blue}{Third, our percent cover data are essentially error-free because we were able to aggregate indiviual plant areas to calculate percent cover.
Percent cover data collected by typical sampling protocals (e.g., Daubenmire frames) will include error that may affect population forecasts due to misspecifing the initial conditions and/or biasing model parameters}
(Queenborough et al. 2011).
\textcolor{blue}{Thus, it may be that our percent cover model performed just as well as the individual-based model because percent cover was perfectly measured.
One way to account for such error is to develop a sampling model that relates the observations (estimated percent cover in a plot) to the true state (percent cover derived from individual plant measurements in the same plot)}
(Hobbs and Hooten 2015).

\textcolor{blue}{Although our main goal was to compare individual-based and population-level modeling approaches relative to one another, it is worth reflecting on the absolute forecasting skill of our models.
In particular, the forecast horizon of both models, defined as the time horizon at which the correlation between predictions and observations falls below $\rho = 0.5$, is less than five years for all species. 
Such short forecast horizons are not encouraging.}
\textcolor{blue}{Unfortunately, we have little to offer on how to improve population forecasts that has not already been proposed}
(Mouquet et al. 2015, Petchey et al. 2015).
\textcolor{blue}{Longer time-series should improve our ability to detect exogenous drivers such as climate}
(Teller et al. 2016),
\textcolor{blue}{and modeling larger spatial extents may reduce parameter uncertainty}
(Petchey et al. 2015).
\textcolor{blue}{We may also have to shift our perspective from making explicit point forecasts to making moving average forecasts}
(Petchey et al. 2015).
\textcolor{blue}{For example, IPMs are typically capable of estimating equilibrium abundances}
(e.g., Adler et al. 2012),
\textcolor{blue}{which may be more appropriate for dynamic systems.}

@@

Hefley, T. J., and M. B. Hooten. 2016. Hierarchical Species Distribution
Models. Current Landscape Ecology Reports 1:87--97.

@@

Mieszkowska, N., G. Milligan, M. T. Burrows, R. Freckleton, and M.
Spencer. 2013. Dynamic species distribution models from categorical
survey data. Journal of Animal Ecology 82:1215--1226.

>>>>

To date, most empirical population modelers have relied on
individual-level data, with few attempts to capitalize on
population-level measures. An important exception was an effort by
Taylor and Hastings (2004) to model the population growth rate of an
invasive species to identify the best strategies for invasion control.
They used a ``density-structured'' model where the state variable is a
discrete density state rather than a continuous density measure. Such
models do not require individual-level demographic data and can
adequately describe population dynamics. Building on Taylor and Hastings
(2004), Freckleton et al. (2011) showed that density-structured models
compare well to continuous models in theory, and Queenborough et al.
(2011) provide empirical evidence that density-structured models are
capable of reproducing population dynamics at landscape spatial scales,
even if some precision is lost when compared to fully continuous models.
However, previous tests of density-structured population models have yet
to assess their ability to forecast out-of-sample observations, and they
have not included environmental covariates, which are necessary to
forecast population responses to climate change.

@@

\textcolor{blue}{We used two types of data: individual-level data and percent cover data.
Using the individual-level data, we fit three vital rate regressions (survival, growth, and rectruitment) to build an Integral Projection Model (IPM) for simulating the plant populations.
Using the percent cover data we fit a simple, Gompertz population growth model, which we refer to as a quadrat-based model (QBM).
For both model types (IPM and QBM), we fit and simulate versions of the model with and without climate covariates.
We used Bayesian ridge regression to weight the importance of each climate covariate.
We then performed cross-validation to assess each model's ability to predict out-of-sample data.
We compared the forecast accuracy ($\rho$, correlation between observations and predictions) and mean absolute error (MAE) between the IPM and the QBM to test our expectation that the IPM should outperform the QBM.
Lastly, we use in-sample forecasts to quantify each model's forecast horizon}
(Petchey et al. 2015).

@@

We fit all models using a hierarchical Bayesian approach. We focus on
the main process and the model likelihood in what follows (full model
descriptions are in the Supporting Information). For the likelihood
models, \(\textbf{y}^X\) is always the relevant vector of observations
for vital rate \emph{X} (\emph{X} = \emph{S}, \emph{G}, \emph{R}, or
\emph{P} for survival, growth, recruitment, or population growth). For
example, \(\textbf{y}^S\) is a vector of 0s and 1s indicating whether a
genet survives from \emph{t} to \emph{t+1}, or not, for all observation
years and quadrats. All model parameters are species-specific, but we
omit subscripts for species in model descriptions below to reduce visual
clutter. For brevity, we only describe models with climate covariates
included, but models without climate covariates are simply the models
described below with the climate effects removed.

@@

An important feature of any forecasting model is the rate at which
forecast skill declines as the time between an observation and a
forecast increases.
\textcolor{blue}{In particular, we are interested in the temporal distance at which forecast skill falls below a threshold: the so-called ecological forecast horizon}
(Petchey et al. 2015). To assess the forecast horizons of our models, we
initiate the forecast model with the population state at some time
\emph{t} and make sequential forecasts of the population at times
\(t+1, t+2, \dots, t+T\) where \emph{T} is the maximum number of years
between the initial year and the final year of our observations. For
example, if we initialize the forecast model with percent cover in 1940,
we are able to make five forecasts up to the year 1945. Forecast models
are not re-initialized with observations between years. Thus, in our
current example, the model forecast for percent cover in 1941 has a
forecast horizon of one year, the forecast in 1942 has a forecast
horizon of two years, and so on. We performed these simulations for all
model types (IPM with/without climate; QBM with/without climate) using
mean parameter values for all possible initial years. For a given
forecast distance, we averaged the correlation between forecasts and
observations. Note that our forecasts for the horizon analysis are all
made using in-sample data because we used model fits from the full data
set. Nonetheless, our simulations offer insight into the differences
among model forecast horizons.
\textcolor{blue}{We chose an arbitrary forecast accuracy of $\rho = 0.5$ as our forecast proficiency threshold.
For basic research on forecasting, arbitrary proficiency thresholds suffice for comparative purposes}
(Petchey et al. 2015),
\textcolor{blue}{and $\rho = 0.5$ represents the point at which about 25% of the variance in observations is explained by the predictions.
So, the forecast horizon is the temporal distance at which forecast accuracy falls below $\rho = 0.5$.}

@@

With climate covariates included
\textcolor{blue}{and using mean parameter values, the accuracy of both models' forecasts declined as the distance between the last observation and the forecast increased},
but they did so at similar rates (Fig. 4). The only exception is for
\emph{Poa secunda}, where QBM forecast accuracy remained steady as the
\textcolor{blue}{temporal distance of the forecast increased}, whereas
IPM forecast accuracy declined (Fig. 4).
\textcolor{blue}{The forecast horizons were short: forecast accuracy fell below $\rho$ = 0.5 after one year for the IPM for most species, and after four years, at most, for the QBM (Fig. 4).
Across the different temporal distances from the observation to the forecast, the IPM was never more accurate than the QBM (\emph{P} > 0.05 for all one-sided \emph{t}-tests, Table S23).
Likewise, the QBM was rarely more accurate the IPM, the only exception being for \emph{H. comata} at temporal distances of two ($t_{(115)}$ = 2.39, \emph{P} = 0.002) and three years ($t_{(98)}$ = 2.04, \emph{P} = 0.022) (Table S24).
There were some cases where the QBM was more accurate than the IPM for \emph{Poa secunda}, but neither model exceeded the forecast profieciency threshold by a large margin (Fig. 4, Table S24).}

@@

We also expected IPM forecast accuracy to decline at a lower rate than
the QBM as the
\textcolor{blue}{time between the model initialization and the forecast increased.}
In principle, more mechanistic models should produce better predictions,
especially under novel conditions (Evans 2012, Schindler and Hilborn
2015). In our case, the IPM explicitly models the influence of weather
on recruitment and survival, effects that may be poorly represented in
the QBM because recruitment and survival mainly affect small plants that
contribute little to year-to-year changes in percent cover. Over time,
the addition and subtraction of small plants can have large effects on
population growth, thus, explicitly modeling these effects could
contribute to a longer forecast horizon. However, we found no evidence
\textcolor{blue}{that the forecast horizon for the IPM was greater than the QBM (Fig. 4).
On the contrary, the QBM tended to have a slightly longer forecast horizon than the IPM for most species (Fig. 4).
The QBM has fewer processes and parameters, which can reduce bias due to parameter uncertainty.
Thus, the QBM may better capture near term dynamics when populations do not fluctuate widely, as in our case.}

Our comparison of a model based on individual-level data with one based
on percent cover data is not an exhaustive test. Understanding the
reasons why the percent cover-based model matched the skill of a
demographic model for our focal species may help us anticipate
situations in which a percent-cover approach would fail. First, for none
of our species did a climate covariate have a strong negative effect on
one vital rate and a strong positive effect on a different vital rate
(Fig. 3). As noted by Freckleton et al. (2011), complex age or stage
structure can compromise predictions from models that aggregate over
life-histories, and the same should be true when aggregating across
vital rates with contrasting responses to climate drivers. Second, our
particular recruitment model is already so aggregated -- it averages
across seed production, germination and establishment -- that it may
fail to detect important demographic responses to climate, putting our
individual-based model and percent cover model on more equal footing.
More finely resolved recruitment data might help our individual-based
model outperform the population-level model. As advocated by Freckleton
et al. (2011), knowledge of a species' population ecology should guide
the modeling approach.
\textcolor{blue}{Third, our percent cover data are essentially error-free because we were able to aggregate indiviual plant areas to calculate percent cover.
Percent cover data collected by typical sampling methods (e.g., Daubenmire frames) will include error that may affect population forecasts due to misspecifing the initial conditions and/or biasing model parameters}
(Queenborough et al. 2011).
\textcolor{blue}{Percent cover models based on data containing more measurement error than ours might perform worse in comparison with individual-based models.
One way to account for such error is to develop a sampling model that relates the observations (estimated percent cover in a plot) to the true state (percent cover derived from individual plant measurements in the same plot)}
(Hobbs and Hooten 2015).

\textcolor{blue}{Although our main goal was to compare individual-based and population-level modeling approaches relative to one another, it is worth reflecting on the absolute forecasting skill of our models.
In particular, the forecast horizon of both models, defined as the time horizon at which the correlation between predictions and observations falls below $\rho = 0.5$, is less than five years for all species. 
Such short forecast horizons are not encouraging.}
\textcolor{blue}{Unfortunately, we have few ideas about how to improve population forecasts that have not already been proposed}
(Mouquet et al. 2015, Petchey et al. 2015).
\textcolor{blue}{Longer time-series should improve our ability to detect exogenous drivers such as climate}
(Teller et al. 2016),
\textcolor{blue}{and modeling larger spatial extents may reduce parameter uncertainty}
(Petchey et al. 2015).
\textcolor{blue}{We may also have to shift our perspective from making explicit point forecasts to making moving average forecasts}
(Petchey et al. 2015).
\textcolor{blue}{Whether the poor predictive ability of our models impacts their comparison relative to one another is an open question}.

@@

@@
